Measurement and Probability in Fuzzy Quantum Theories

### 2016-11-25 proposal/prop.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background III: From Functions to Interactive Processes}

@@

\item Going further we actually have to concede not just the infinite
  accuracy of the quantum state, but its very existence as a ``real''
  entity that exists independently of measurements and
  probabilities. The reasons for this radical position are as
  follows. First arguments embedded in the proof of the Kochen-Specker
  theorem essentially rule out the existence of a sample space as the
  probabilities of events cannot be consistently expressed using core
  assignments to elements of the sample space. Second, the frequency
  interpretation of probability which is already problematic in the
  classical case, becomes untenable in the quantum case. In both
  cases, but much more in the quantum case, it is much more sensible
  to interpret probability in the Bayesian sense as ``lack of
  knowledge''. This, and similar arguments elegantly expressed by
  recent work on Quantum Bayesianism~\cite{}, suggest that the quantum
  state is more like an interactive system in computer science
  parlance. In other words, the state is only determined by its
  interactions with the environment or observers. A rough but useful
  analogy in the context of computer science would be a web server:
  the state of such a system cannot be said to exist independently of
  the interactions with clients; each interaction with a client
  determines a future state of the system and may affect future
  interactions. Crucially, each client may have a \emph{different}
  view of the web server that is consistent with their own history of
  interactions. This computational perspective agrees with the
  philosophical position of QBism that asserts that the quantum state
  is subjective: each observer has a different view of the quantum
  system that is consistent with their previous observations and that
  allows that observer, independently of other observers, to assign
  beliefs (i.e., probabilities) to future interactions.

@@

%%%%%
\subsection{Proposed Activity I: Quantum Interval-valued Probability Measures}

@@

%%%%%
\subsection{Proposed Activity II: Quantum Information Theorems}

@@

%%%%%
\subsection{Proposed Activity III: Quantum States as Interactive Processes}

background III is classical; do quantum version; application to CS and
quantum information

>>>>

@@

\item Going further we actually have to concede not just the infinite
  accuracy of the quantum state, but its very existence as a ``real''
  entity that exists independently of measurements and
  probabilities. The reasons for this radical position are as
  follows. First arguments embedded in the proof of the Kochen-Specker
  theorem essentially rule out the existence of a sample space as the
  probabilities of events cannot be consistently expressed using core
  assignments to elements of the sample space. Second, the frequency
  interpretation of probability which is already problematic in the
  classical case, becomes untenable in the quantum case. In both
  cases, but much more in the quantum case, it is much more sensible
  to interpret probability in the Bayesian sense as ``lack of
  knowledge''. This, and similar arguments elegantly expressed by
  recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016},
  suggest that the quantum state is more like an interactive system in
  computer science parlance. In other words, the state is only
  determined by its interactions with the environment or observers. A
  rough but useful analogy in the context of computer science would be
  a web server: the state of such a system cannot be said to exist
  independently of the interactions with clients; each interaction
  with a client determines a future state of the system and may affect
  future interactions. Crucially, each client may have a
  \emph{different} view of the web server that is consistent with
  their own history of interactions. This computational perspective
  agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
  that asserts that the quantum state is subjective: each observer has
  a different view of the quantum system that is consistent with their
  previous observations and that allows that observer, independently
  of other observers, to assign beliefs (i.e., probabilities) to
  future interactions.

@@

%%%%
\subsection{Proposed Activity I: Quantum States as Interactive Processes}

do quantum version; application to CS and quantum information

%%%%%
\subsection{Proposed Activity II: Quantum Interval-valued Probability Measures}

@@

%%%%%
\subsection{Proposed Activity III: Quantum Information Theorems}

@@

%%%%%
\subsection{Proposed Activity IV: Computational Aspects}
